Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-14 SRO_Retest_Analyses.Rmd
working on analyses

Quick check to make sure there isn't anything weird with anonymization of retest data

```{r}
last_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/retest_worker_lookup.json')

old_lookup1 <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/old/worker_lookup_3.json')

old_lookup2 <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/old/worker_lookup_8.json')

process_lookup <- function(lookup_json){
  lookup_json <- data.frame(unlist(lookup_json))
  lookup_json$sub_id <- as.character(row.names(lookup_json))
  row.names(lookup_json) <- seq(1:nrow(lookup_json))
  names(lookup_json)[1] <- 'worker_id'
  lookup_json$worker_id <- as.character(lookup_json$worker_id)
  lookup_json$complete <- ifelse(lookup_json$worker_id == lookup_json$sub_id, 0, 1)
  lookup_json <- lookup_json %>% arrange(-complete, sub_id)
  return(lookup_json)
}

last_lookup <- process_lookup(last_lookup)
old_lookup1 <- process_lookup(old_lookup1)
old_lookup2 <- process_lookup(old_lookup2)

old_lookup1[old_lookup1$complete == 1, 'worker_id'] == last_lookup[1:68, 'worker_id'] 
old_lookup2[old_lookup2$complete == 1, 'worker_id'] == last_lookup[1:113, 'worker_id']

rm(last_lookup, old_lookup1, old_lookup2)
```

Extract retest participants
```{r}
test_worker_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/worker_lookup.json')

retest_worker_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_Data_NewApi/retest_worker_lookup.json')

#Process full lookup tables for both datasets
test_worker_lookup <- process_lookup(test_worker_lookup)
retest_worker_lookup <- process_lookup(retest_worker_lookup)

@@

#Trim lookup tables to only include those we have data for
retest_worker_lookup <- retest_worker_lookup[retest_worker_lookup$sub_id %in% retest_data$sub_id,]

test_worker_lookup <- test_worker_lookup[test_worker_lookup$sub_id %in% test_data$sub_id,]

#Are all retest workers in test data?
retest_worker_lookup$worker_id %in% test_worker_lookup$worker_id
```

One retest participant is not in test data. Remove that subject from lookup table and from retest_data
```{r}
retest_worker_lookup <- retest_worker_lookup[retest_worker_lookup$worker_id %in% test_worker_lookup$worker_id,]

retest_data <- retest_data[retest_data$sub_id %in% retest_worker_lookup$sub_id,]
```

Id match df
```{r}
id_match_df <- merge(retest_worker_lookup, test_worker_lookup, by='worker_id', all.x=T)

id_match_df <- id_match_df %>%
  select(-complete.x, -complete.y) %>%
  rename(retest_sub_id = sub_id.x, test_sub_id = sub_id.y) %>%
  arrange(retest_sub_id)

sub_id_lookup <- id_match_df %>% select(-worker_id)
write.csv(sub_id_lookup, 'sub_id_lookup.csv')
rm(sub_id_lookup)
```

Extract test data for retest subjects, add worker_id column to both datasets and arrange by worker_id, check if the rows match
```{r}
test_data <- merge(id_match_df, test_data, by.x='test_sub_id', by.y='sub_id', all.x=T)
retest_data <- merge(id_match_df, retest_data, by.x='retest_sub_id', by.y='sub_id', all.x=T)
test_data <- test_data %>% arrange(worker_id)
retest_data <- retest_data %>% arrange(worker_id)
test_data$worker_id == retest_data$worker_id
```

@@

Retest data columns that are not in the original data:

```{r}
names(retest_data)[names(retest_data) %in% names(test_data) == FALSE]
```

Test data columns that are not in the retest data:
(as expected; three by two is not added yet)
```{r}
names(test_data)[names(test_data) %in% names(retest_data) == FALSE]
```

@@

```{r}
all_columns <- unique(c(names(test_data), names(retest_data)))

matching_columns <- c()
for(i in 1:length(all_columns)){
  if(all_columns[i] %in% names(test_data) & all_columns[i] %in% names(retest_data)){
    matching_columns <- c(matching_columns, all_columns[i])
  }
}

matching_retest_data <- retest_data[,matching_columns]
matching_test_data <- test_data[,matching_columns]
```

@@

 - First data release email esp to ASU
 - Send the spreadsheet with meaningul variables + demographics
 - Fix the worker id's not sharing

>>>>

Function to process lookup table
```{r}
process_lookup <- function(lookup_json){
  lookup_json <- data.frame(unlist(lookup_json))
  lookup_json$sub_id <- as.character(row.names(lookup_json))
  row.names(lookup_json) <- seq(1:nrow(lookup_json))
  names(lookup_json)[1] <- 'worker_id'
  lookup_json$worker_id <- as.character(lookup_json$worker_id)
  lookup_json$complete <- ifelse(lookup_json$worker_id == lookup_json$sub_id, 0, 1)
  lookup_json <- lookup_json %>% arrange(-complete, sub_id)
  return(lookup_json)
}
```

Extract retest participants from test data

```{r}
test_worker_lookup <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/Local/worker_lookup.json')

#Process full lookup tables for both datasets
test_worker_lookup <- process_lookup(test_worker_lookup)

@@

#Trim lookup table to only include those we have data for
test_worker_lookup <- test_worker_lookup[test_worker_lookup$sub_id %in% test_data$sub_id,]

#Replace worker_id's in retest_data with original sub_id's 
correct_subids <- function(row, lookup_table){
  sub_id = row$sub_id
  if(sub_id %in% lookup_table$worker_id){
    index = which(sub_id == lookup_table$worker_id)
    sub_id = lookup_table$sub_id[index]
    row$sub_id = sub_id
  }
  return(row)
}

retest_data <- retest_data %>%
  group_by(sub_id) %>%
  do(correct_subids(.,test_worker_lookup))

#Are all retest subjects in test_data? No. 
sum(retest_data$sub_id %in% test_data$sub_id) == nrow(retest_data)

#Who is missing?
retest_data$sub_id[which(retest_data$sub_id %in% test_data$sub_id == FALSE)]
```

One retest participant is not in test data. Remove that subject from retest_data for now
```{r}
retest_data <- retest_data[retest_data$sub_id %in% test_data$sub_id,]

retest_data
```

Extract test data for retest subjects
```{r}
retest_subs_test_data <- test_data[test_data$sub_id %in% retest_data$sub_id,]

rest_subs_test_data <- test_data[test_data$sub_id %in% retest_data$sub_id == FALSE,]

#Arrange datasets of same size by sub_id
retest_data = retest_data %>% arrange(sub_id)
retest_subs_test_data = retest_subs_test_data %>% arrange(sub_id)

#CHECK IF EVERYTHING IS ORDERED RIGHT
retest_subs_test_data$sub_id == retest_data$sub_id
```

@@

Are there any columns in retest data columns that are not in the original data: No.

```{r}
names(retest_data)[names(retest_data) %in% names(retest_subs_test_data) == FALSE]
```

Test data columns that are not in the retest data: Two stage hasn't been fixed yet.

```{r}
names(retest_subs_test_data)[names(retest_subs_test_data) %in% names(retest_data) == FALSE]
```

@@

```{r}
all_columns <- unique(c(names(retest_data), names(retest_subs_test_data)))

matching_columns <- c()
for(i in 1:length(all_columns)){
  if(all_columns[i] %in% names(retest_data) & all_columns[i] %in% names(retest_subs_test_data)){
    matching_columns <- c(matching_columns, all_columns[i])
  }
}

retest_data <- retest_data[,matching_columns]
retest_subs_test_data <- retest_subs_test_data[,matching_columns]
```

@@

 - First data release email esp to ASU
 - Send the spreadsheet with meaningul variables + demographics
